\documentclass{beamer}
\def\Put(#1,#2)#3{\leavevmode\makebox(0,0){\put(#1,#2){#3}}}
\usepackage{tabularx, booktabs}
\usetheme{Frankfurt}
\usepackage{caption}
\usepackage{color}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{pdfpages}
\usepackage{hyperref}


\captionsetup[table]{labelformat = empty}
\setbeamertemplate{navigation symbols}{} % Suppress the navigation symbols that normally appear on the bottom of Beamer slides

% Redefine the footer to three-panel split with Author | Title | Slide number instead of Warsaw default
\makeatletter
\setbeamertemplate{footline}
{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshortauthor%~~\beamer@ifempty{\insertshortinstitute}{}{(\insertshortinstitute)}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
    \usebeamerfont{title in head/foot}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}%
   % \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}
    \insertframenumber{} / \inserttotalframenumber\hspace*{2ex} 
  \end{beamercolorbox}}%
  \vskip0pt%
}
\makeatother


\title{Open Payments: Financial Transparency Between Medical Providers and Manufacturers}
\author{Vincent La}
\institute{Code for San Francisco}
\date{\today}

\begin{document}

\maketitle

\begin{frame}
\label{Overview}
\frametitle{Overview}
What is Open Payments?
\begin{enumerate}
\item[1.] Program created by the Affordable Care Act to increase transparency of payments to medical providers from manufacturers
\newline
\item[2.] Financial Conflicts of Interests for Medical Providers
%This includes gifts, meals, drug samples. Promotional speakers for the company
\newline
\item[3.] Summary Statistics (2014)\footnote{https://openpaymentsdata.cms.gov/summary}

\begin{itemize}
\item \$6.45 Billion total payments
\item 607,000 Providers
\item 1,122 Teaching Hospitals
\end{itemize}

\end{enumerate}
\end{frame}

\begin{frame} 
\frametitle{Why do we care? A Real Life Example: Vioxx (Merck)}
Financial Conflict of Interests $\Rightarrow$ Clinical Trials?\footnote{http://www.jabfm.org/content/18/5/414.full.pdf}
\begin{enumerate}
\item Approved 1999 by the FDA, Vioxx treated patients with arthritis and other conditions causing chronic or acute pain
\item Prescribed to over 80 million patients
\item Study published in NEJM, submitted to the FDA, failed to report patients taking Vioxx were 21\% more likely to develop serious illnesses than patients taking the generic counterpart
\item \textbf{All 13 authors had financial ties or were employed by Merck.}
\item Summary of timeline of events\footnote{http://www.npr.org/templates/story/story.php?storyId=5470430}
\end{enumerate}
\end{frame}

\begin{frame} 
\frametitle{Why do we care?}
Financial Conflict of Interests $\Rightarrow$ Medical Practice?
\begin{enumerate}
\item In a survey of 3,100 physicians, 94\% report some financial relationship with industry in the previous year.\footnote{http://www.ncbi.nlm.nih.gov/books/NBK22944/}

\begin{enumerate}
\item Meals: 83\%
\item Drug Samples: 78\%
\item Industry Reimbursement for professional meetings: 35\%
\item Consulting/Speaking Fees/Clinical Trials: 28\%
\end{enumerate}

\item Transfers exceeding \$1000 from a pharmaceutical company to a physician resulted in 60 additional prescriptions per year by that physician for drugs manufactured by the company.\footnote{http://rady.ucsd.edu/faculty/directory/engelberg/pub/portfolios/doctors.pdf}
\end{enumerate}
\end{frame}

\begin{frame} 
\frametitle{What can we do?}
\begin{enumerate}
\item Open Payments Data: https://www.cms.gov/OpenPayments/Explore-the-Data/Data-Overview.html
\item Build a Search Tool: Better lookup tool (by NPI, geographic location, physician specialty, etc.)
\item \textbf{Data Visualization}
\end{enumerate}
\end{frame}

\begin{frame} 
\frametitle{Project Idea: Data Visualization}
While CMS's provided search tool could use better features, I think there's a lot of opportunity for interesting data visualizations.

\begin{enumerate}
\item Create a heat map showing payment ``hot spots" geographically at a general level
\item At a local level, allow people to zoom into a certain geographical area and show a list of actual providers with the amount of money they receive from manufacturers (think Zillow map of house values)
\textbf{Goal: Better information dissemination; allow patients to better shop around for high-value care!}
\item Example of some data visualizations with healthcare data: http://www.dartmouthatlas.org/
\end{enumerate}
\end{frame}

\begin{frame} 
\frametitle{Conclusion}
GitHub: \url{https://github.com/VincentLa/open\_payments}
\newline
Contact Info: vincela14@gmail.com
\end{frame}

\end{document}
